Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

\extraspacing {\bf Generating $\bm{\J_2}$.} Take any $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v) \in \J(R_1, ..., R_{k-3}, H', V)$. Note that $\bm{t}[k-2] = h'$ must intersect with $v$, because $\bm{t}$ is a result tuple of the $(k-1)$-SJ on $R_1, ..., R_{k-3}, H', V$. Suppose $h = [x_1, x_2] \times y$ and $p = (x, y)$ is the intersection point between $h$ and $v$, we define the {\em effective horizontal segment} of $\bm{t}$ as the horizontal segment $h' = [x_1, x] \times y$.
\myeqn{
    \contained_{R_{k-2}}(\bm{t}) &=& \{r \in R_{k-2} \mid \text{ the effective horizontal } \nn \\
    && \text{segment of $\bm{t}$ is contained in $r$}   \}
    \label{eqn:type2:contained-t}
}
The above definition should not be confused with \eqref{eqn:contained}, where the $\contained$ function takes a horizontal segment as the input.

>>>>

\extraspacing {\bf Generating $\bm{\J_2}$.} Take any $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v) \in \J(R_1, ..., R_{k-3}, H', V)$. Note that $\bm{t}[k-2] = h'$ must intersect with $v$, because $\bm{t}$ is a result tuple of the $(k-1)$-SJ on $R_1, ..., R_{k-3}, H', V$. Suppose $h = [x_1, x_2] \times y$ and $p = (x, y)$ is the intersection point between $h$ and $v$, we define the {\em effective horizontal segment} of $\bm{t}$ as the horizontal segment $h' = [x_1, x] \times y$.
\myeqn{
    \contained_{R_{k-2}}(\bm{t}) &=& \{r \in R_{k-2} \mid \text{ the effective horizontal } \nn \\
    && \text{segment of $\bm{t}$ is contained in $r$}   \}
    \label{eqn:type2:contained-t}
}
The above should not be confused with \eqref{eqn:contained}, where the ``$\contained$'' function takes a segment as the input, rather than a tuple.
